---
title: "Component Order in Learning from Verbal Information"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
    encoding=encoding,
    output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Anton Koger"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: TRUE
    toc_float: TRUE
    toc_depth: 3
    number_sections: TRUE
  pdf_document: default
  word_document: default
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Preparations

## Plugins 
```{r dat4, echo=TRUE, out.extra='hide', warning=FALSE, message=FALSE}
library(emmeans)
library(ggpubr)
library(Rmisc)
library(dplyr)
library(data.table)
library(psych)
library(afex)
library(ggplot2)
```


## Importing Data 
```{r}
# set working directory
setwd("C:/Users/anton/OneDrive - Students RWTH Aachen University/Uni Master/5_UiT/Experiments/data")


# create list with all files with the task from all versions
file_list = list.files(pattern = "*.csv") 
# import these files to one list
df_list = lapply(file_list, read.csv)
# add all data frames in this list into one data frame
data = rbindlist(df_list, fill = TRUE)
# clean up
rm(file_list, df_list)

# save original data in dataset
data_original = data
```


## Renaming and Adding Variables
```{r}

# renaming
data = rename(data,
             effectPrime = trialType, 
             compOrderCode = sentenceOrder,
             compOrder = sentenceOrderText,
             verbalResp = colorKey,
             meanError_ID = meanError,
             meanRT_ID = meanRT)

# new variable for required response
data = mutate(data, reqResp = cor_resp)
# and now change the lables
data = mutate(data, reqResp = case_when(reqResp == "Q" ~ "left",
                                        reqResp == "P" ~ "right"))

# new variable for age
data = mutate(data, age = 2022 - data$yearBorn)

```



## Preparing Data
```{r}
# only keep main trials and rows in which a response was made
# (exclude instructions, practice trials, fixation, and error feedback)
data_main = filter(data, blockType == "main")

# delete too slow responses
data_main = mutate(data_main, tooSlow = case_when(respValue == "q" ~ 0,
                                                  respValue == "p" ~ 0,
                                                  TRUE ~ 1))

data_main = filter(data_main, tooSlow != 1)

# change data type of rt from chr to int
# note: there are NA, as no rt are present when responses were too slow
data_main = mutate(data_main, rt = as.numeric(rt))

# factorize data
data_main = data_main %>%
  mutate(ID = as.factor(ID),
         verbalResp = as.factor(verbalResp),
         reqResp = as.factor(reqResp),
         effectPrime = as.factor(effectPrime),
         compOrder = as.factor(compOrder))

# some participants wrote their age instead of the year of birth
data_main = data_main %>%
  mutate(yearBorn = case_when(yearBorn == 26 ~ 1996,
                              yearBorn == 28 ~ 1994,
                              yearBorn == 36 ~ 1986,
                              yearBorn == 50 ~ 1972,
                              TRUE ~ as.numeric(as.character(yearBorn))))



```



## First Look
```{r}
# aggregate dataset per participant (while discarding later excluded participants)
data_agg = data_original %>%
  filter(ID != "ecdrnqhw" &
           ID != "cppygz8l" &
           ID != "wzgg40tc") %>%
    mutate(yearBorn = case_when(yearBorn == 26 ~ 1996,
                              yearBorn == 28 ~ 1994,
                              yearBorn == 36 ~ 1986,
                              yearBorn == 50 ~ 1972,
                              TRUE ~ as.numeric(as.character(yearBorn)))) %>%
  group_by(ID) %>%
  summarise(balancing = mean(balancing),
            balancingText = first(balancingText),
            sentenceOrder = mean(sentenceOrder),
            sentenceOrderText = first(sentenceOrderText),
            colorKey = first(colorKey),
            meanRT = first(meanRT),
            meanError_RT = first(meanError),
            gender = first(gender),
            yearBorn = first(yearBorn),
            age = 2022 - first(yearBorn))

# check balancing
table(data_agg$balancingText)
table(data_agg$sentenceOrderText)
table(data_agg$colorKey)


# look at mean rt and error rates
# # change rt variable type
# data$rt = as.numeric(data$rt)
# # only keep main trials with a response
# data = data %>%
#   filter(blockType == "main")
# error rates
mean(data_main$error)
sd(data_main$error)
# rt
mean(data_main$rt, na.rm = TRUE)
sd(data_main$rt, na.rm = TRUE)


##### Step 1: get familiar with the data ####
summary(data)
describe(data)

# lets see how many pp we have
uniqueN(data$ID)

# lets check how many trials each pp has
count(data, ID)



###for RT per pp###
# mean RT per pp in a Boxplot
boxplot(tapply(data_main$rt, data_main$ID, mean))$out
# scatterplot
plot(tapply(data_main$rt, data_main$ID, mean))


###for errors per pp###
# mean error per pp in a Boxplot
boxplot(tapply(data_main$error, data_main$ID, mean))$out
# there are 2 pp with higher error rates (above 20%)
# and a scatterplot
plot(tapply(data_main$error, data_main$ID, mean))

hist(tapply(data_main$error, data_main$ID, mean))



```



# Data Cleaning 

- Participants showing random responses (~50% errors and above) will be removed. 
- Participants that are "extrem" outliers (boxplot, 3*IQR) on mean response times or mean error rate will be removed.
- Participants having more than 10% of responses below 300 ms will be removed.
- For response time analyses, response errors will be removed.
- Response times below 150 ms will be excluded from the analysis.
- Individual response times that are beyond 3*SD above/below the mean (calculated per participant and within participant condition) will be removed.

## Remove Participants With Extrem Outliers (Errors and RT) and Random Responses
```{r}
### Participants showing random responses (~50% errors and above) will be removed. 
### Participants that are "extrem" outliers (boxplot, 3*IQR) on mean response times or mean error rate will be removed.
# mean RT per pp in a Boxplot
boxplot(tapply(data_main$rt, data_main$ID, mean),
        main="Mean RT per Participant",
        ylab="RT in ms")
# mean error per pp in a Boxplot
boxplot(tapply(data_main$error, data_main$ID, mean)*100,
        main="Mean Errors per Participant",
        ylab="Error Rate in %")

# Participants above 40% errors
names(which(tapply(data_main$error, data_main$ID, mean) > .4))
# Removing participants who had around 50% errors
data_main = filter(data_main, ID != "ecdrnqhw" &
                              ID != "cppygz8l")
# delete empty factor levels
data_main$ID = droplevels(data_main$ID)


### Participants having more than 10% of responses below 300 ms will be removed.
# create new variable which tells us if the RT was below 300ms
data_main = data_main %>%
  group_by(ID) %>%
  mutate(rtBelow300 = ifelse(rt < 300, 1, 0))
# now count how many times this happens per participant 
# and only show those, where it happens more than 10% (9 times)
names(which(tapply(data_main$rtBelow300, data_main$ID, sum) > 9))
# Removing participant who had more than 10% of the responses faster than 300 ms
data_main = filter(data_main, ID != "wzgg40tc")
# delete empty factor levels
data_main$ID = droplevels(data_main$ID)


### Response times below 150 ms will be excluded from the analysis.
data_main = filter(data_main, rt > 150)


### For response time analyses, response errors will be removed.
data_main_rt = filter(data_main, error == 0)


### Individual response times that are beyond 3*SD above/below the mean (calculated per participant and within participant condition) will be removed.
# add mean and SD of RT per participant and within condition into new columns
data_main_rt = data_main_rt %>%
  ungroup() %>%
  mutate(meanRTcell = ave(data_main_rt$rt, 
                          list(data_main_rt$ID, data_main_rt$reqResp, data_main_rt$effectPrime), 
                          FUN = mean),
         sdRTcell = ave(data_main_rt$rt, 
                          list(data_main_rt$ID, data_main_rt$reqResp, data_main_rt$effectPrime), 
                          FUN = sd))
# add column which codes whether a trial is an outlier
data_main_rt = data_main_rt %>%
  mutate(outlierRT = case_when(rt > (meanRTcell + 3*sdRTcell) ~ 1,
                               rt < (meanRTcell - 3*sdRTcell) ~ 1,
                               TRUE ~ 0))
# delete trials which are an RT outlier 
data_main_rt = filter(data_main_rt, outlierRT == 0)


```



## Demographic info 
```{r}

# tables 
table(data_agg$gender)

table(data_agg$age)

mean(data_agg$age)
sd(data_agg$age)
range(data_agg$age)




```


# Analysis

## Error Rates

### Preparation (Data Aggregation)
```{r}
# aggregate dataset for error analysis
data_main_error_agg = data_main %>%
  group_by(ID, verbalResp, reqResp, effectPrime, compOrder) %>%
  summarise(meanError = mean(error)); show(data_main_error_agg)


```


### Error Analysis (4-Way)
```{r}

# ez ANOVA
aov_error = aov_ez(id = "ID",
                   dv = "meanError",
                   data = data_main_error_agg,
                   between = c("compOrder", "verbalResp"),
                   within = c("reqResp", "effectPrime")); show(aov_error)


## means
meanError <- summarySEwithin(data_main_error_agg, measurevar = 'meanError',
                          withinvars = c("reqResp", "effectPrime"),
                          betweenvars = c("compOrder", "verbalResp"),
                          idvar = 'ID',
                          na.rm = T); head(meanError)

# (meanError_2 = data_main_error_agg %>%
#     ungroup() %>%
#     group_by(verbalResp, reqResp, effectPrime, compOrder) %>%
#     summarise(error = mean(meanError)) %>%
#     mutate(error = as.numeric(error)*100))


```



### Error Analysis (3-Way)
```{r}

# ez ANOVA for Effect-Action Order
aov_error_effect_action = aov_ez(id = "ID",
                                 dv = "meanError",
                                 data = filter(data_main_error_agg, compOrder == "effect_action"),
                                 between = c("verbalResp"),
                                 within = c("reqResp", "effectPrime")); show(aov_error_effect_action)

# ez ANOVA for Action-Effect Order
aov_error_action_effect = aov_ez(id = "ID",
                                 dv = "meanError",
                                 data = filter(data_main_error_agg, compOrder == "action_effect"),
                                 between = c("verbalResp"),
                                 within = c("reqResp", "effectPrime")); show(aov_error_action_effect)

```



### Error Analysis (2-Way) and Contrasts
```{r}

### Effect-Action Order
## Prime critical
aov_error_effect_action_effectPrime_critical = aov_ez(id = "ID",
                                                     dv = "meanError",
                                                     data = filter(data_main_error_agg, compOrder == "effect_action" &
                                                                     effectPrime == "critical"),
                                                     between = c("verbalResp"),
                                                     within = c("reqResp")); show(aov_error_effect_action_effectPrime_critical)

# now contrasts with these results
emmeans(aov_error_effect_action_effectPrime_critical, ~ reqResp * verbalResp)
(contrasts_error_effect_action_effectPrime_critical_reqResp_x_verbalResp = pairs(emmeans(aov_error_effect_action_effectPrime_critical, ~ reqResp * verbalResp)))

## Prime neutral
aov_error_effect_action_effectPrime_neutral = aov_ez(id = "ID",
                                                     dv = "meanError",
                                                     data = filter(data_main_error_agg, compOrder == "effect_action" &
                                                                     effectPrime == "neutral"),
                                                     between = c("verbalResp"),
                                                     within = c("reqResp")); show(aov_error_effect_action_effectPrime_neutral)

# # now contrasts with these results
# emmeans(aov_error_effect_action_effectPrime_neutral, ~ reqResp * verbalResp)
# (contrasts_error_effect_action_effectPrime_neutral_reqResp_x_verbalResp = pairs(emmeans(aov_error_effect_action_effectPrime_neutral, ~ reqResp * verbalResp)))


### Action-Effect Order
## Prime critical
aov_error_action_effect_effectPrime_critical = aov_ez(id = "ID",
                                                     dv = "meanError",
                                                     data = filter(data_main_error_agg, compOrder == "action_effect" &
                                                                     effectPrime == "critical"),
                                                     between = c("verbalResp"),
                                                     within = c("reqResp")); show(aov_error_action_effect_effectPrime_critical)

# now contrasts with these results
emmeans(aov_error_action_effect_effectPrime_critical, ~ reqResp * verbalResp)
(contrasts_error_action_effect_effectPrime_critical_reqResp_x_verbalResp = pairs(emmeans(aov_error_action_effect_effectPrime_critical, ~ reqResp * verbalResp)))

## Prime neutral
aov_error_action_effect_effectPrime_neutral = aov_ez(id = "ID",
                                                     dv = "meanError",
                                                     data = filter(data_main_error_agg, compOrder == "action_effect" &
                                                                     effectPrime == "neutral"),
                                                     between = c("verbalResp"),
                                                     within = c("reqResp")); show(aov_error_action_effect_effectPrime_neutral)

# # now contrasts with these results
# emmeans(aov_error_action_effect_effectPrime_neutral, ~ reqResp * verbalResp)
# (contrasts_error_effect_action_effectPrime_neutral_reqResp_x_verbalResp = pairs(emmeans(aov_error_action_effect_effectPrime_neutral, ~ reqResp * verbalResp)))




```




### Graphs Errors
```{r}

# Effect-Action Order
plot_error_effect_action = 
  ggplot(filter(meanError, compOrder == "effect_action"),
         aes(x=reqResp, y=meanError, fill=verbalResp)) +
  geom_bar(stat = "summary", fun = mean, position = 'dodge', color = 'black', size = .8) + 
  geom_errorbar(aes(ymin=meanError-ci, ymax=meanError+ci),
                width=.2,
                size= .5,
                position=position_dodge(.9)) +
  facet_grid(.~ effectPrime) +
  coord_cartesian(ylim = c(0, 0.16)) +                                                                  # <---
  scale_y_continuous(breaks=c(0, 0.02, 0.04, 0.06, 0.08, 0.1, 0.12, 0.14, 0.16), expand = c(0, 0)) +    # <---
  scale_fill_manual(values=c("white", "gray40"))+
  xlab('Required response') +
  ylab('Mean proportion of errors') +
  guides(fill=guide_legend(title="Instructed response")) +
  ggtitle("Effect-action order") +
  theme(panel.border = element_blank(),
        plot.title            = element_text(size = 20, face = "bold", hjust = 0.5),
        legend.position       = 'none',                                                 #c(0.75, 0.8),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.title          = element_text(size  = 18, face="bold"),
        legend.text           = element_text(size  = 18),
        legend.box.background = element_rect(fill  = "white"),
        plot.background       = element_rect(fill  = "white"),
        panel.background      = element_rect(fill  = "white"),
        axis.line.x           = element_line(colour  = "black"),                       # <---
        axis.line.y           = element_line(colour  = "black"),                       # <---
        axis.title.x          = element_text(size  = 18),                              #,hjust = 0.5, vjust = -0.5),
        axis.title.y          = element_text(size  = 18),                              #,hjust = 0.5, vjust = 2),
        #plot.title            = element_text(hjust = 0.5), 
        strip.text.x          = element_text(size  = 18, color = 'black'),
        axis.text.x           = element_text(size  = 18, color = 'black'),
        axis.text.y           = element_text(size  = 16, color = 'black')
  ); plot_error_effect_action


# Action-Effect Order
plot_error_action_effect = 
  ggplot(filter(meanError, compOrder == "action_effect"),
         aes(x=reqResp, y=meanError, fill=verbalResp)) +
  geom_bar(stat = "summary", fun = mean, position = 'dodge', color = 'black', size = .8) + 
  geom_errorbar(aes(ymin=meanError-ci, ymax=meanError+ci),
                width=.2,
                size= .5,
                position=position_dodge(.9)) +
  facet_grid(.~ effectPrime) +
  coord_cartesian(ylim = c(0, 0.16)) +                                                                  # <---
  scale_y_continuous(breaks=c(0, 0.02, 0.04, 0.06, 0.08, 0.1, 0.12, 0.14, 0.16), expand = c(0, 0)) +    # <---
  scale_fill_manual(values=c("white", "gray40"))+
  xlab('Required response') +
  ylab('Mean proportion of errors') +
  guides(fill=guide_legend(title="Instructed response")) +
  ggtitle("Action-effect order") +
  theme(panel.border = element_blank(),
        plot.title            = element_text(size = 20, face = "bold", hjust = 0.5),
        legend.position       = 'none',                                                 #c(0.75, 0.8),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.title          = element_text(size  = 18, face="bold"),
        legend.text           = element_text(size  = 18),
        legend.box.background = element_rect(fill  = "white"),
        plot.background       = element_rect(fill  = "white"),
        panel.background      = element_rect(fill  = "white"),
        axis.line.x           = element_line(colour  = "black"),                       # <---
        axis.line.y           = element_line(colour  = "black"),                       # <---
        axis.title.x          = element_text(size  = 18),                              #,hjust = 0.5, vjust = -0.5),
        axis.title.y          = element_text(size  = 18),                              #,hjust = 0.5, vjust = 2),
        #plot.title            = element_text(hjust = 0.5), 
        strip.text.x          = element_text(size  = 18, color = 'black'),
        axis.text.x           = element_text(size  = 18, color = 'black'),
        axis.text.y           = element_text(size  = 16, color = 'black')
  ); plot_error_action_effect



## Combined
plot_error = ggarrange(plot_error_effect_action, plot_error_action_effect,
                             labels = c('a.', 'b.'), ncol = 2, nrow = 1,  common.legend = F); plot_error

```




## Reaction Times 

### Preparation (Data Aggregation)

```{r}
# aggregate dataset for error analysis
data_main_rt_agg = data_main_rt %>%
  group_by(ID, verbalResp, reqResp, effectPrime, compOrder) %>%
  summarise(meanRT = mean(rt)); show(data_main_rt_agg)


```

### Reaction Time Analysis (4-Way)
```{r}

# ez ANOVA
aov_rt = aov_ez(id = "ID",
                dv = "meanRT",
                data = data_main_rt_agg,
                between = c("compOrder", "verbalResp"),
                within = c("reqResp", "effectPrime")); show(aov_rt)


## means 
meanRT <- summarySEwithin(data_main_rt_agg, measurevar = 'meanRT',
                          withinvars = c("reqResp", "effectPrime"),
                          betweenvars = c("compOrder", "verbalResp"),
                          idvar = 'ID',
                          na.rm = T); head(meanRT)

# (meanRT_2 = data_main_rt_agg %>%
#     ungroup() %>%
#     group_by(verbalResp, reqResp, effectPrime, compOrder) %>%
#     summarise(rt = mean(meanRT)))


```


### Reaction Time Analysis (3-Way)
```{r}

# ez ANOVA for Effect-Action Order
aov_rt_effect_action = aov_ez(id = "ID",
                                 dv = "meanRT",
                                 data = filter(data_main_rt_agg, compOrder == "effect_action"),
                                 between = c("verbalResp"),
                                 within = c("reqResp", "effectPrime")); show(aov_rt_effect_action)

# ez ANOVA for Action-Effect Order
aov_rt_action_effect = aov_ez(id = "ID",
                                 dv = "meanRT",
                                 data = filter(data_main_rt_agg, compOrder == "action_effect"),
                                 between = c("verbalResp"),
                                 within = c("reqResp", "effectPrime")); show(aov_rt_action_effect)


```




### Reaction Time Analysis (2-Way) and Contrasts
```{r}

### Effect-Action Order
## Prime critical
aov_rt_effect_action_effectPrime_critical = aov_ez(id = "ID",
                                                     dv = "meanRT",
                                                     data = filter(data_main_rt_agg, compOrder == "effect_action" &
                                                                     effectPrime == "critical"),
                                                     between = c("verbalResp"),
                                                     within = c("reqResp")); show(aov_rt_effect_action_effectPrime_critical)

# now contrasts with these results
emmeans(aov_rt_effect_action_effectPrime_critical, ~ reqResp * verbalResp)
(contrasts_rt_effect_action_effectPrime_critical_reqResp_x_verbalResp = pairs(emmeans(aov_rt_effect_action_effectPrime_critical, ~ reqResp * verbalResp)))

## Prime neutral
aov_rt_effect_action_effectPrime_neutral = aov_ez(id = "ID",
                                                     dv = "meanRT",
                                                     data = filter(data_main_rt_agg, compOrder == "effect_action" &
                                                                     effectPrime == "neutral"),
                                                     between = c("verbalResp"),
                                                     within = c("reqResp")); show(aov_rt_effect_action_effectPrime_neutral)

# # now contrasts with these results
# emmeans(aov_rt_effect_action_effectPrime_neutral, ~ reqResp * verbalResp)
# (contrasts_rt_effect_action_effectPrime_neutral_reqResp_x_verbalResp = pairs(emmeans(aov_rt_effect_action_effectPrime_neutral, ~ reqResp * verbalResp)))


### Action-Effect Order
## Prime critical
aov_rt_action_effect_effectPrime_critical = aov_ez(id = "ID",
                                                     dv = "meanRT",
                                                     data = filter(data_main_rt_agg, compOrder == "action_effect" &
                                                                     effectPrime == "critical"),
                                                     between = c("verbalResp"),
                                                     within = c("reqResp")); show(aov_rt_action_effect_effectPrime_critical)

# now contrasts with these results
emmeans(aov_rt_action_effect_effectPrime_critical, ~ reqResp * verbalResp)
(contrasts_rt_action_effect_effectPrime_critical_reqResp_x_verbalResp = pairs(emmeans(aov_rt_action_effect_effectPrime_critical, ~ reqResp * verbalResp)))

## Prime neutral
aov_rt_action_effect_effectPrime_neutral = aov_ez(id = "ID",
                                                     dv = "meanRT",
                                                     data = filter(data_main_rt_agg, compOrder == "action_effect" &
                                                                     effectPrime == "neutral"),
                                                     between = c("verbalResp"),
                                                     within = c("reqResp")); show(aov_rt_action_effect_effectPrime_neutral)

# # now contrasts with these results
# emmeans(aov_rt_action_effect_effectPrime_neutral, ~ reqResp * verbalResp)
# (contrasts_rt_effect_action_effectPrime_neutral_reqResp_x_verbalResp = pairs(emmeans(aov_rt_action_effect_effectPrime_neutral, ~ reqResp * verbalResp)))




```



### Graphs Reaction Times
```{r}

# Effect-Action Order
plot_rt_effect_action = 
  ggplot(filter(meanRT, compOrder == "effect_action"),
         aes(x = reqResp, y = meanRT, fill = verbalResp)) +
  geom_bar(stat = "summary", fun = mean, position = 'dodge', color = 'black', size = .8) + 
  geom_errorbar(aes(ymin = meanRT - ci, ymax = meanRT + ci),
                width = .2,
                size = .5,
                position=position_dodge(.9)) +
  facet_grid(.~ effectPrime) +
  coord_cartesian(ylim = c(500, 600)) +                                                                  # <---
  scale_fill_manual(values=c("white", "gray40"))+
  xlab('Required response') +
  ylab('Mean response times (ms)') +
  guides(fill=guide_legend(title="Instructed response")) +
  ggtitle("Effect-action order") +
  theme(panel.border = element_blank(),
        plot.title            = element_text(size = 20, face = "bold", hjust = 0.5),
        legend.position       = 'none',                                                 #c(0.75, 0.8),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.title          = element_text(size  = 18, face="bold"),
        legend.text           = element_text(size  = 18),
        legend.box.background = element_rect(fill  = "white"),
        plot.background       = element_rect(fill  = "white"),
        panel.background      = element_rect(fill  = "white"),
        axis.line.x           = element_line(colour  = "black"),                       # <---
        axis.line.y           = element_line(colour  = "black"),                       # <---
        axis.title.x          = element_text(size  = 18),                              #,hjust = 0.5, vjust = -0.5),
        axis.title.y          = element_text(size  = 18),                              #,hjust = 0.5, vjust = 2),
        #plot.title            = element_text(hjust = 0.5), 
        strip.text.x          = element_text(size  = 18, color = 'black'),
        axis.text.x           = element_text(size  = 18, color = 'black'),
        axis.text.y           = element_text(size  = 16, color = 'black')
  ); plot_rt_effect_action


# Action-Effect Order
plot_rt_action_effect = 
  ggplot(filter(meanRT, compOrder == "action_effect"),
         aes(x = reqResp, y = meanRT, fill = verbalResp)) +
  geom_bar(stat = "summary", fun = mean, position = 'dodge', color = 'black', size = .8) + 
  geom_errorbar(aes(ymin = meanRT - ci, ymax = meanRT + ci),
                width=.2,
                size= .5,
                position=position_dodge(.9)) +
  facet_grid(.~ effectPrime) +
  coord_cartesian(ylim = c(500, 600)) +                                                                  # <---
  scale_fill_manual(values=c("white", "gray40"))+
  xlab('Required response') +
  ylab('Mean response times (ms)') +
  guides(fill=guide_legend(title="Instructed response")) +
  ggtitle("Action-effect order") +
  theme(panel.border = element_blank(),
        plot.title            = element_text(size = 20, face = "bold", hjust = 0.5),
        legend.position       = 'none',                                                 #c(0.75, 0.8),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.title          = element_text(size  = 18, face="bold"),
        legend.text           = element_text(size  = 18),
        legend.box.background = element_rect(fill  = "white"),
        plot.background       = element_rect(fill  = "white"),
        panel.background      = element_rect(fill  = "white"),
        axis.line.x           = element_line(colour  = "black"),                       # <---
        axis.line.y           = element_line(colour  = "black"),                       # <---
        axis.title.x          = element_text(size  = 18),                              #,hjust = 0.5, vjust = -0.5),
        axis.title.y          = element_text(size  = 18),                              #,hjust = 0.5, vjust = 2),
        #plot.title            = element_text(hjust = 0.5), 
        strip.text.x          = element_text(size  = 18, color = 'black'),
        axis.text.x           = element_text(size  = 18, color = 'black'),
        axis.text.y           = element_text(size  = 16, color = 'black')
  ); plot_rt_action_effect



## Combined
plot_rt = ggarrange(plot_rt_effect_action, plot_rt_action_effect,
                             labels = c('a.', 'b.'), ncol = 2, nrow = 1,  common.legend = F); plot_rt

```


